MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-09-26 chapters/MetaTracts.tex
Updated XBundle Bib and  supplemental material

Lomov et al.~\cite{Lomov2010, Lomov2001} and Straumit et al.~\cite{StraumitI2014} in recent papers, discussed the problems and current available solutions in geometric modeling of three dimensional composites. Modeling of the composites, first starts with establishing the topology of the structure, which translates to answering if a particular bundle is in contact with another at a particular position? The second step builds the geometry of the model, answering questions relating to placement of bundles in space their orientations and dimensions.

@@

The input to the first stage of our pipeline, is the original scalar dataset in a uniform lattice grid in $\mathbb{R}^3$. As output, each grid location becomes associated with a vector representing the local orientation and a real value [0,1] that represents a measure of the reliability of the local orientation. We approximate the local orientation by eigenvalue analysis of the Hessian matrix computed at each voxel. The principal directions, in which the local second order structure of the image can be decomposed, are given by the eigen decomposition of the Hessian matrix which describes the local curvature.
The eigenvector corresponding to the smallest eigenvalue gives the direction along which the curvature is smallest. This direction coincides with the direction of the tubular structure.

>>>>

Lomov et al.~\cite{Lomov2010, Lomov2001} and Straumit et al.~\cite{Straumit2014} in recent papers, discussed the problems and current available solutions in geometric modeling of three dimensional composites. Modeling of the composites, first starts with establishing the topology of the structure, which translates to answering if a particular bundle is in contact with another at a particular position? The second step builds the geometry of the model, answering questions relating to placement of bundles in space their orientations and dimensions.

@@

The input to the first stage of our pipeline, is the original scalar dataset in a uniform lattice grid in $\mathbb{R}^3$. As output, each grid location becomes associated with an unit vector representing the local orientation and a real value [0,1] that represents a measure of the reliability of the local orientation. We approximate the local orientation by eigenvalue analysis of the Hessian matrix computed at each voxel.
The Hessian matrix represents the local curvature. The eigen decomposition of the Hessian matrix gives the eigenvectors which describe the local second-order structure of the image.

The eigenvector corresponding to the smallest eigenvalue gives the direction along which the curvature is smallest. This direction coincides with the direction of the tubular structure.

### 2014-09-26 supplemental/supplementaryMaterial.tex
Updated XBundle Bib and  supplemental material

\section{Supplementary Material}
\label{sec:sm}
Section~\ref{subsec:ext_exp} contains extended experiments.
Section~\ref{subsec:usereval} contains our user evaluation questionnaire.
\subsection{Extended Experiments}
\label{subsec:ext_exp}

>>>>

\section{Supplementary Material}
\label{sec:sm}
Section~\ref{subsec:ext_exp} contains extended experiments.
Section~\ref{subsec:usereval} contains our user evaluation questionnaire.
\subsection{Enlarged Figures}
\label{subsec:enlarged_fig}
\begin{figure}[tb]
	\centering
	%\includegraphics[width=0.5\textwidth, trim = 0mm 110mm 0mm 0mm, clip,]{images_pvis/figure1}
	\includegraphics[width=\textwidth]{images_pvis/data-char.pdf}
	\caption{Data characteristics: (a) Rendering of the data. (b) 2D slices along the X-axis and (c) 2D slice along the Z-axis. (d) Magnified region marked in green square (c). Multiple fiber bundles cross and are indistinguishable by visual inspection alone. }
	\label{fig:data-char}
\end{figure}
\subsection{Extended Experiments}
\label{subsec:ext_exp}
